A Reduced Order Model for Porous Media Flows: Coupling Linear Regression with Principal Component Analysis (PCA) using High-Order Singular Value Decomposition (HOSVD) in Upscaling Calculations for Permeability in Reservoir Simulations

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

\subsubsection{Understanding the permeability space}\label{subsubsection:visualization_permspace}
Permeability can be represented as either tensor or scalar quantity, however for the purpose of the following explanation (and the remaining of this work), permeability is assumed as a scalar quantity. Furthermore, the simulator prescribes the permeability field by assigning permeability values to the centre of element-pairs \cite{Christou_2018} which discretises the simulation domain.

Permeability values assigned in the centre of the element/cell represents values of permeability for the associated element $\left(\text{\ie P}_{0}\text{DG element-pair}\right)$. For simplicity, in the remaining part of this sub-section, a $2D$ geometry is assumed where the geometry is discritized by a square grid with the value for each square element assigned in the centre of the element. This explanation allow one to easily visualize this permeability space because it is defined by the cartesian coordinates system.

>>>>

\subsubsection{Understanding the permeability space}\label{subsubsection:visualization_permspace}
Permeability can be represented as either tensor or scalar quantity, however for the purpose of the following explanation (and the remaining of this work), permeability is assumed as a scalar quantity. In addition, in the numerical simulations performed for this work, permeability is discretised element-wise with projection to the control volume space within each element-pairs (see \cite{Christou_2018}). Permeability values are assigned to the centre of the FE $\left(\text{\ie P}_{0}\text{DG element-pair}\right)$. For simplicity, in the remaining part of this sub-section, a $2D$ geometry is assumed which is discretized with triangular elements (\PN[1]{2} and \PNDG[1]{1} element-pairs). This explanation allows one to easily visualize this permeability space because it is defined by Cartesian coordinate system.
